%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://lukeshadler.tech/}{\Large Lucas Shadler}} & Email : \href{mailto:lshadler13@gmail.com}{lshadler13@gmail.com}\\
  \href{http://lukeshadler.tech/}{http://lukeshadler.tech} & Mobile : +1-585-766-7886 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technologyy}{Rochester, NY}
      {Bachelors in Physics; Minors: Computer Science, Math, Electrical Engineering  GPA: 3.9}{Aug. 2013 -- Jun. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Solu Technology Partners}{Rochester, NY}
      {Full StackSoftware Engineer}{July 2017 - Present}
      \resumeItemListStart
        \resumeItem{Scrum Team}
          {Work as a member of an Agile Scrum team to provide state-of-the-art Angular 2 Material Applications, with daily code reviews to maintain a fast-paced agenda}
        \resumeItem{Spring/MySQL}
          {Integrate a MySQL database architecture with front-end components using the Spring framework, Java Persistence, and RESTful API.}
      \resumeItemListEnd

    \resumeSubheading
      {WiTricity Corporation}{Boston, MA}
      {R\&D Engineer (Co-Op)}{Jan 2014 - Oct 2016}
      \resumeItemListStart
        \resumeItem{Wireless Power Transfer}
          {Developed auxiliary systems to prevent foreign object and living object intervention within the field to aid in the safety of wireless power transfer.}
        \resumeItem{Embedded Systems Firmware}
          {Produced a serial method of transferring data from a PSoC5 microcontroller reading sensor measuremACents into real-time and offline datasets.}
        \resumeItem{PCB Prototyping}
          {Used Altium PCB designer to create new and space-efficient prototype boards for sensor development and positioning. Holders and caps for the designs were 3D modeled using Solidworks.}
        \resumeItem{Machine Learning}
          {Created trained models for position detection using machine learning techniques in python using the toolkit SKLearn. Developed a method to adapt the model in real time to provide directives for position alignment.}
        \resumeItem{Robotics}
          {Developed a CNC for consistent and persistent testing over a wide range of sensor positions, programmed to be interactively controlled by a Python GUI.}
      \resumeItemListEnd

    \resumeSubheading
      {Laser Interferometer Gravitational-Wave Observatory @ Caltech}{Pasadena, CA}
      {Astrophysicist}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Gravitational Wave Astronomy}
          {Recieved training on the design behind the most sensitive detector made by mankind and how to extract relevant Gravitational Wave information from it.}
        \resumeItem{Multi-threaded Programming (OpenMP)}
          {Used an Open Source to create a performance-oriented method of filtering signal data by utilizing multi-threaded CPUs.}
        \resumeItem{Presentation and Reporting}
          {Completed the project with a publishable scientific report, as well as a presentation given to the entire LIGO collaboration.}
      \resumeItemListEnd

    \resumeSubheading
      {FermiLab}{Chicago, IL}
      {High Energy Particle Physicist}{Fall 2014 - Summer 2015}
      \resumeItemListStart
        \resumeItem{Particle Tracking Algorithm}
          {Produced an algorithm in C++ to recreate the path of a Proton from a Neutrino interation using CCD data within MINERvA}
        \resumeItem{Team-specific Legacy Framework}
          {Utilized framework structure created previously by other scientists to augment the algorithm such that the algorithm could be used on incoming data from the detector}
        \resumeItem{Large Team Communication}
          {Experience in navigating a large volume of collaborators, seeking assistance only where needed.}
      \resumeItemListEnd

    \resumeSubheading
      {Lab for Multiwavelength Astrophysics @ RIT}{Rochester, NY}
      {Astrophysicist}{2013-2017}
      \resumeItemListStart
        \resumeItem{3D data modeling}
          {Visualized 3D Morpho-kinematic models of nearby Galaxy NGC1386 in the interest of characterizing the mechanism by which its Supermassive Black Hole accretes matter.}
        \resumeItem{Workshop Teaching}
          {Taught a workshop class at Universidade Federal do Rio Grande do Sul based on the modeling techniques used.}
      \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Personal Website}
      {Static website produced using the Jekyll framework, complete with version control, a blogging system, templating, and continuous integration. }
    \resumeSubItem{Pollaroid}
      {An Open Source tool to allow users to reach out to their local representatives and participate in political polls.}

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
